\documentclass[a4paper,11pt]{article}

\usepackage{res}
\hypersetup{pdftitle={Dennies Bor - Software Engineering \& Cloud CV}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Dennies Bor}} & Email: \href{mailto:dbor@gmu.edu}{dbor@gmu.edu}\\
  GitHub: \href{https://github.com/denniesbor}{github.com/denniesbor} & LinkedIn: \href{https://linkedin.com/in/denniesbor}{linkedin.com/in/denniesbor} \\
  Website: \href{https://denniesbor.com}{denniesbor.com} & Scholar: \href{https://scholar.google.com/citations?user=mnet84cAAAAJ}{Google Scholar} \\
\end{tabular*}

\section{Professional Summary}
Software engineer with a scientific-computing background, building and deploying full-stack applications, dashboards, and reproducible research tooling. Experienced with cloud deployment, CI/CD automation, containerization, and Linux-based operations for reliable delivery of data products.

\section{Skills Summary}
\resumeSubHeadingListStart
  \resumeSubItem{Frontend}{React, modern SPA workflows, dashboard UI/UX, visualization-driven interfaces.}
  \resumeSubItem{Backend \& APIs}{REST patterns, data-serving endpoints, automation scripts and pipeline tooling.}
  \resumeSubItem{Cloud \& DevOps}{AWS, Docker, Nginx, systemd, GitHub Actions (CI/CD), Linux administration.}
  \resumeSubItem{Data Products}{Reproducible data pipelines, batch processing, packaging research artifacts for delivery.}
  \resumeSubItem{Engineering Practices}{Git workflows, structured repos, documentation-first shipping, release automation.}
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {George Mason University}{Fairfax, VA, USA}
    {PhD in Earth Systems and Geoinformation Sciences (Advisor: Dr. Edward Oughton)}{Sep 2023 -- Present}
    {\footnotesize\textit{\textbf{Relevant Coursework:} Computational Physics, Earth Image Processing, GIS Algorithms, Spatial Computing}}\\
    {\footnotesize\textit{\textbf{GPA:} 3.96}}
  \resumeSubheading
    {Technical University of Kenya}{Nairobi, Kenya}
    {BEng in Aeronautical Engineering (First Class Honors)}{Sep 2013 -- May 2019}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading{Graduate Research Assistant}{George Mason University, VA, USA}
  {Research Software, Dashboards, Deployment Automation}{May 2022 -- Present}
  \resumeItemListStart
    \item Developed interactive web-based GIS and research dashboards for infrastructure resilience and risk analysis.
    \item Built deployment-ready research artifacts (data pipelines + UI) and maintained reproducible workflows for sharing results.
    \item Automated build/release pipelines using GitHub Actions; containerized components where appropriate.
  \resumeItemListEnd

  \resumeSubheading{Engineering Intern}{Broglio Space Center, Malindi, Kenya}
  {Satellite Operations, Remote Sensing}{Aug 2018 -- Nov 2018}
  \resumeItemListStart
    \item Supported satellite tracking and telemetry for geospatial applications.
    \item Assisted in the maintenance and operation of RF communication systems.
  \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects \& Proposals}
\resumeSubHeadingListStart

  \resumeSubItem{Portfolio Platform and Research Dashboards (\textbf{denniesbor.github.io})}
  {\href{https://github.com/denniesbor/denniesbor.github.io}{GitHub} \,|\, \href{https://denniesbor.me}{Live}}

  \resumeSubItem{Reproducible Grid Mapping Dashboard (\textbf{spw-geophy-io})}
  {\href{https://arxiv.org/abs/2412.17685}{Preprint} \,|\, \href{https://github.com/denniesbor/spw-geophy-io}{GitHub} \,|\, \href{https://denniesbor.github.io/spw-geophy-io/}{Dashboard}}

  \resumeSubItem{Coupled Space Weather Impact Model (\textbf{C-SWIM})}
  {\href{https://arxiv.org/abs/2412.18032}{Preprint} \,|\, \href{https://github.com/denniesbor/C-SWIM}{GitHub} \,|\, \href{https://denniesbor.me/portfolio/space-weather-grid}{Dashboard}}

  \resumeSubItem{Ops Automation Utilities (\textbf{linux\_sys\_admin\_scripts})}
  {\href{https://github.com/denniesbor/linux_sys_admin_scripts}{GitHub}}

  \resumeSubItem{Computer Vision for Power Substation Asset Detection (\textbf{substation-assets-identification})}
  {\href{https://github.com/denniesbor/substation-assets-identification}{GitHub}}

\resumeSubHeadingListEnd

\section{Professional Affiliations}
\resumeSubHeadingListStart
  \resumeSubheading
    {National Center for Atmospheric Research}{USA}
    {Early Career Faculty Innovators Program}{2023 -- 2025}
  \resumeSubheading
    {African Institute of Mathematical Sciences}{South Africa}
    {Africa Data Science Intensive Program}{2022}
\resumeSubHeadingListEnd

\section{References}
Available upon request.

\end{document}
