\documentclass[a4paper,11pt]{article}
\usepackage{res}

\hypersetup{pdftitle={Dennies Bor - Academic CV}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Dennies Bor}} & Email: \href{mailto:dbor@gmu.edu}{dbor@gmu.edu}\\
  Computational Scientist & LinkedIn: \href{https://linkedin.com/in/denniesbor}{linkedin.com/in/denniesbor} \\
  \href{https://denniesbor.com}{denniesbor.com} & Scholar: \href{https://scholar.google.com/citations?user=mnet84cAAAAJ}{Google Scholar} \\
\end{tabular*}

\section{Research Interests}
Computational Physics, Infrastructure Resilience, Space Weather Impact Assessment, Magnetotellurics, Geospatial Intelligence.

\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {George Mason University}{Fairfax, VA, USA}
      {PhD in Earth Systems and Geoinformation Sciences (Advisor: Dr. Edward Oughton)}{Sep 2023 -- Present}
      {\footnotesize\textit{\textbf{GPA:} 3.96 | \textbf{Coursework:} Computational Physics, Applied Electromagnetics, Spatial Computing}}
      
    \resumeSubheading
      {Technical University of Kenya}{Nairobi, Kenya}
      {BEng in Aeronautical Engineering (First Class Honors)}{Sep 2013 -- May 2019}
\resumeSubHeadingListEnd

\section{Research Experience}
\resumeSubHeadingListStart
  \resumeSubheading{Graduate Research Assistant}{George Mason University}
  {Center for Earth Systems and Geoinformation Sciences}{May 2022 -- Present}
  \resumeItemListStart
    \item Developing a coupled Physics-Engineering-Economic pipeline to quantify U.S. power grid vulnerability to extreme space weather events.
    \item Implemented Computable General Equilibrium (CGE) models using nonlinear optimization to assess cascading socio-economic impacts of infrastructure failure.
    \item Utilizing high-performance computing (AWS/HPC) to process 100-year extreme event scenarios for transmission network topology.
  \resumeItemListEnd
  
  \resumeSubheading{Engineering Intern}{Broglio Space Center}
  {Satellite Operations \& RF Systems}{Aug 2018 -- Nov 2018}
  \resumeItemListStart
    \item Supported telemetry tracking and RF communication systems for Earth observation missions.
  \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Selected Publications \& Preprints}
\resumeSubHeadingListStart
  \resumeSubItem{Mapping Electricity Infrastructure}
  {A Reproducible Method for Mapping Electricity Transmission Infrastructure for Space Weather Risk Assessment. \href{https://arxiv.org/abs/2412.17685}{arXiv:2412.17685}}
  \resumeSubItem{Socio-economic Impact Modeling}
  {A Physics-Engineering-Economic Model Coupling Approach for Estimating Socio-economic Impacts of Space Weather. \href{https://arxiv.org/abs/2412.18032}{arXiv:2412.18032}}
\resumeSubHeadingListEnd

\section{Technical Skills}
\resumeSubHeadingListStart
  \resumeSubItem{Scientific Computing}{Python (NumPy, SciPy, Pyomo), MATLAB, Finite Difference Methods (FDM), ODE/PDE Solvers.}
  \resumeSubItem{Geospatial Analysis}{GDAL, Geopandas, Rasterio, Cesium.js, Spatial Statistics (Moran's I, GWR).}
  \resumeSubItem{Machine Learning}{YOLOv8, TensorFlow, PyTorch, Computer Vision.}
  \resumeSubItem{DevOps}{Docker, AWS (EC2), Git/GitHub Actions, Linux/Unix (Fedora/Ubuntu).}
\resumeSubHeadingListEnd

\end{document}