\documentclass[a4paper,11pt]{article}

\usepackage{res}
\hypersetup{pdftitle={Dennies Bor - Data Science \& ML CV}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Dennies Bor}} & Email: \href{mailto:dbor@gmu.edu}{dbor@gmu.edu}\\
  GitHub: \href{https://github.com/denniesbor}{github.com/denniesbor} & LinkedIn: \href{https://linkedin.com/in/denniesbor}{linkedin.com/in/denniesbor} \\
  Website: \href{https://denniesbor.com}{denniesbor.com} & Scholar: \href{https://scholar.google.com/citations?user=mnet84cAAAAJ}{Google Scholar} \\
\end{tabular*}

\section{Professional Summary}
Data science \& machine learning practitioner with strengths in time-series modeling, signal processing, and applied ML for scientific and infrastructure systems. Experienced in building reproducible pipelines, benchmarking models against classical baselines, and communicating results via dashboards and open-source code.

\section{Technical Skills}
\resumeSubHeadingListStart
  \resumeSubItem{Machine Learning}{Deep learning (CNN/GRU/LSTM, attention), physics-informed learning, object detection (YOLO), feature engineering, model benchmarking.}
  \resumeSubItem{Statistics \& Uncertainty}{Probabilistic simulation (Monte Carlo), hypothesis testing, sensitivity analysis, error analysis and validation workflows.}
  \resumeSubItem{Time Series \& Signal Processing}{Frequency-domain analysis, matched filtering concepts, coherence estimation, Welch PSD, spectral features.}
  \resumeSubItem{Scientific Programming}{Python (NumPy, SciPy, Pandas, Matplotlib), PyTorch/TensorFlow (project-dependent), reproducible notebooks and scripts.}
  \resumeSubItem{Data \& Tooling}{Git, Linux, Docker, GitHub Actions; experiment organization, logging, and result tracking.}
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {George Mason University}{Fairfax, VA, USA}
    {PhD in Earth Systems and Geoinformation Sciences (Advisor: Dr. Edward Oughton)}{Sep 2023 -- Present}

  \begin{itemize}[leftmargin=*,label={},itemsep=1pt,topsep=2pt]
    \item \small{\textbf{Selected Coursework:} Quantitative Methods; Earth Sci Data / Advanced Data Analysis; Digital Signal Processing; Computational Physics II; Remote Sensing.}
    \item \small{\textbf{GPA:} 3.85}
  \end{itemize}
  \vspace{-6pt}
  
  \resumeSubheading
    {Technical University of Kenya}{Nairobi, Kenya}
    {BEng in Aeronautical Engineering (First Class Honors)}{Sep 2013 -- May 2019}
\resumeSubHeadingListEnd

\section{Research Experience}
\resumeSubHeadingListStart
  \resumeSubheading{Graduate Research Assistant}{George Mason University, VA, USA}
  {ML-Enabled Risk Modeling, Time Series, Spatial Data Products}{May 2022 -- Present}
  \resumeItemListStart
    \item Built reproducible research pipelines integrating observational data, predictive modeling, and validation for infrastructure and space-environment risk studies.
    \item Developed benchmarking workflows comparing classical models (e.g., transfer functions / physics baselines) against ML approaches on real event datasets.
  \resumeItemListEnd

  \resumeSubheading{Engineering Intern}{Broglio Space Center, Malindi, Kenya}
  {Satellite Operations, RF Systems}{Aug 2018 -- Nov 2018}
  \resumeItemListStart
    \item Supported satellite tracking, telemetry processing, and RF communication system operations for Earth observation missions.
  \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Selected Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading{\textbf{tfpy}: GIC Prediction Model Benchmarking \,|\, \href{https://github.com/denniesbor/tfpy}{tfpy}}{}
  \resumeItemListStart
    \item Comparative evaluation of traditional transfer-function methods versus neural network approaches for geomagnetically induced current prediction.
    \item Implemented deep learning variants (CNN/GRU/LSTM with attention) and physics-informed modeling components; organized reproducible runs for analysis.
  \resumeItemListEnd

  \resumeProjectHeading{\textbf{substation-assets-identification}: Substation Asset Identification (YOLO) \,|\, \href{https://github.com/denniesbor/substation-assets-identification}{substation-assets-identification}}{}
  \resumeItemListStart
    \item Object detection workflow for identifying substation assets (e.g., transformers) in overhead imagery using YOLO.
    \item Curated project structure for training/inference and repeatable experimentation.
  \resumeItemListEnd

  \resumeProjectHeading{\textbf{twitter\_political\_polarization}: Polarization via Sentiment Analysis \,|\, \href{https://github.com/denniesbor/twitter_political_polarization}{twitter\_political\_polarization}}{}
  \resumeItemListStart
    \item Large-scale sentiment analysis of political discourse across policy topics; statistical comparison across groups.
    \item Results dashboard: \href{https://denniesbor.github.io/twitter_political_polarization/}{twitter\_political\_polarization}.
  \resumeItemListEnd

  \resumeProjectHeading{\textbf{C-SWIM}: Coupled Space Weather Impact Model \,|\, \href{https://github.com/denniesbor/C-SWIM}{C-SWIM}}{}
  \resumeItemListStart
    \item End-to-end pipeline coupling space-weather hazard scenarios, power-grid response modeling, and socio-economic impact estimation.
    \item Dashboard: \href{https://denniesbor.me/portfolio/space-weather-grid}{space-weather-grid}.
  \resumeItemListEnd

\resumeSubHeadingListEnd

\section{Selected Publications \& Preprints}
\resumeSubHeadingListStart
  \resumeSubItem{Quantifying Political Polarization on Key Policy Issues Using Sentiment Analysis (Primary Author)}
  {\href{https://doi.org/10.48550/arXiv.2302.07775}{arXiv:2302.07775} \,|\, Results: \href{https://denniesbor.github.io/twitter_political_polarization/}{twitter\_political\_polarization} \,|\, Code: \href{https://github.com/denniesbor/twitter_political_polarization}{twitter\_political\_polarization}}

  \resumeSubItem{Socio-economic impact of electricity grid infrastructure failure due to severe space weather events (Primary Author)}
  {\href{https://arxiv.org/abs/2412.18032}{arXiv:2412.18032} \,|\, Code: \href{https://github.com/denniesbor/C-SWIM}{C-SWIM} \,|\, Dashboard: \href{https://denniesbor.me/portfolio/space-weather-grid}{space-weather-grid}}

  \resumeSubItem{A Reproducible Method for Mapping Electricity Transmission Infrastructure for Space Weather Risk Assessment (Co-Author)}
  {\href{https://arxiv.org/abs/2412.17685}{arXiv:2412.17685}}

  \resumeSubItem{GIC-Related Observations During the May 2024 Geomagnetic Storm in the United States (Co-Author)}
  {\href{https://arxiv.org/abs/2507.07009}{arXiv:2507.07009}}
\resumeSubHeadingListEnd

\section{Professional Development}
\resumeSubHeadingListStart
  \resumeSubheading
    {National Center for Atmospheric Research}{Boulder, CO, USA}
    {Early Career Faculty Innovators Program}{2023 -- 2025}
  \resumeSubheading
    {African Institute of Mathematical Sciences}{Cape Town, South Africa}
    {Africa Data Science Intensive Program}{2022}
\resumeSubHeadingListEnd

\section{References}
Available upon request.

\end{document}
