\documentclass[a4paper,11pt]{article}

\usepackage{res}

\hypersetup{pdftitle={Dennies Bor CV}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Dennies Bor}} & Email: \href{mailto:dbor@gmu.edu}{dbor@gmu.edu}\\
  GitHub: \href{https://github.com/denniesbor}{github.com/denniesbor} & LinkedIn: \href{https://linkedin.com/in/denniesbor}{linkedin.com/in/denniesbor} \\
  Website: \href{https://denniesbor.com}{denniesbor.com} & Scholar: \href{https://scholar.google.com/citations?user=mnet84cAAAAJ}{Google Scholar} \\
\end{tabular*}

\section{Professional Summary}
Computational scientist specializing in numerical modeling, high-performance computing, and infrastructure resilience analysis. Expertise in developing physics-based simulations, econometric models, and spatial algorithms. Strong background in scientific computing (Python, Pyomo, IPOPT), parallel computing workflows, and cloud-based HPC infrastructure.

\section{Technical Skills}
\resumeSubHeadingListStart
  \resumeSubItem{Computational Physics}{Numerical methods (Euler, RK4, SOR), finite difference methods, particle dynamics, PDEs, electromagnetic field simulations.}
  \resumeSubItem{Signal Processing}{Frequency-domain analysis, matched filters, coherence estimation, Welch PSD, spectral methods.}
  \resumeSubItem{Econometric Modeling}{Input-Output models, Computable General Equilibrium (CGE), nonlinear optimization (Pyomo, IPOPT), uncertainty quantification.}
  \resumeSubItem{Remote Sensing \& Computer Vision}{Hyperspectral imaging, multispectral analysis, satellite image processing, deep learning for object detection (YOLO, CNNs), LiDAR processing.}
  \resumeSubItem{Geospatial Computing}{GIS algorithms, spatial analysis (GDAL, geopandas, rasterio), web mapping (Cesium, Leaflet), point cloud processing.}
  \resumeSubItem{Scientific Programming}{Python (NumPy, SciPy, Matplotlib, Pandas, TensorFlow, PyTorch), Go, React, MATLAB, parallel computing, cloud HPC (AWS EC2).}
  \resumeSubItem{DevOps \& Infrastructure}{Docker, GitHub Actions (CI/CD), Nginx, systemd, AWS deployment, REST APIs.}
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {George Mason University}{Fairfax, VA, USA}
      {PhD in Earth Systems and Geoinformation Sciences (Advisor: Dr. Edward Oughton)}{Sep 2023 -- Present}

      {\footnotesize\textit{\textbf{Relevant Coursework:} Computational Physics, Applied Electromagnetics, Atmospheric Physics, Earth Image Processing, Spatial Computing, Hyperspectral Imaging, GIS Algorithms}}\\
      {\footnotesize\textit{\textbf{GPA:} 3.96}}
      
    \resumeSubheading
      {Technical University of Kenya}{Nairobi, Kenya}
      {BEng in Aeronautical Engineering (First Class Honors)}{Sep 2013 -- May 2019}
\resumeSubHeadingListEnd

\section{Research Experience}
\resumeSubHeadingListStart
  \resumeSubheading{Graduate Research Assistant}{George Mason University, VA, USA}
  {Computational Modeling, Spatial Analysis, Infrastructure Resilience}{May 2022 -- Present}
  \resumeItemListStart
    \item Develop computational models integrating numerical simulations, econometric analysis, and geospatial processing to quantify infrastructure resilience and socio-economic impacts of natural hazards.
  \resumeItemListEnd
  
  \resumeSubheading{Engineering Intern}{Broglio Space Center, Malindi, Kenya}
  {Satellite Operations, RF Systems}{Aug 2018 -- Nov 2018}
  \resumeItemListStart
    \item Supported satellite tracking, telemetry processing, and RF communication systems for Earth observation missions.
    \item Assisted in ground station operations and real-time data acquisition for geospatial applications.
  \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Selected Publications \& Preprints}
\resumeSubHeadingListStart
  \resumeSubItem{A Reproducible Method for Mapping Electricity Transmission Infrastructure for Space Weather Risk Assessment}
  {\href{https://arxiv.org/abs/2412.17685}{arXiv:2412.17685} | Interactive Dashboard: \href{https://denniesbor.github.io/spw-geophy-io/}{denniesbor.github.io/spw-geophy-io}}
  \vspace{2pt}

  \resumeSubItem{A Physics-Engineering-Economic Model Coupling Approach for Estimating Socio-economic Impacts of Space Weather}
  {\href{https://arxiv.org/abs/2412.18032}{arXiv:2412.18032} | Code: \href{https://github.com/denniesbor/C-SWIM}{github.com/denniesbor/spw-geophy-io}}
\resumeSubHeadingListEnd

\section{Professional Development}
\resumeSubHeadingListStart
  \resumeSubheading
    {National Center for Atmospheric Research}{Boulder, CO, USA}
    {Early Career Faculty Innovators Program}{2023 -- 2025}
  \resumeSubheading
    {African Institute of Mathematical Sciences}{Cape Town, South Africa}
    {Africa Data Science Intensive Program}{2022}
\resumeSubHeadingListEnd

\section{References}
Available upon request.

\end{document}